---
title: "Penguins"
output: github_document
---

[https://github.com/allisonhorst/palmerpenguins Palmer Penguins example](https://github.com/allisonhorst/palmerpenguins) as comma separated value files.



```{r}
penguins <- read.table(
  'https://raw.githubusercontent.com/JohnMount/Penguins/main/penguins.csv', 
  header = TRUE, 
  sep = ',', 
  quote = '"')

print(dim(penguins))

knitr::kable(head(penguins))
```


```{r}
penguins_raw <- read.table(
  'https://raw.githubusercontent.com/JohnMount/Penguins/main/penguins_raw.csv', 
  header = TRUE, 
  sep = ',', 
  quote = '"')

print(dim(penguins_raw))

knitr::kable(head(penguins_raw))
```


Palmer Penguins data from:

  [https://github.com/allisonhorst/palmerpenguins](https://github.com/allisonhorst/palmerpenguins)

>citation("palmerpenguins")
>
> To cite palmerpenguins in publications use:
>
>   Gorman KB, Williams TD, Fraser WR (2014) Ecological Sexual Dimorphism
>   and Environmental Variability within a Community of Antarctic
>   Penguins (Genus Pygoscelis). PLoS ONE 9(3): e90081.
>   https://doi.org/10.1371/journal.pone.0090081
>
> A BibTeX entry for LaTeX users is
>
>   @Article{,
>     title = {Ecological Sexual Dimorphism and Environmental Variability within a Community of Antarctic Penguins (Genus Pygoscelis)},
>     author = {Gorman KB and Williams TD and Fraser WR},
>     journal = {PLoS ONE},
>     year = {2014},
>     volume = {9(3)},
>     number = {e90081},
>     pages = {-13},
>     url = {https://doi.org/10.1371/journal.pone.0090081},
>   }


Saved using `R`:

    # install.packages("remotes")
    remotes::install_github("allisonhorst/palmerpenguins")
    write.csv(penguins, 'penguins.csv', row.names = FALSE, quote = FALSE)
    write.csv(penguins_raw, 'penguins_raw.csv', row.names = FALSE, quote = TRUE)

Exported so Python users can also use this data (original package doesn't seem to currently export a csv).


This page found here: [https://github.com/JohnMount/Penguins](https://github.com/JohnMount/Penguins)

Python example here: [https://github.com/JohnMount/Penguins/blob/main/Penguins.ipynb](https://github.com/JohnMount/Penguins/blob/main/Penguins.ipynb)
